You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-31 paper/paper.tex
incorporated more of bill's feedback

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
%\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{A rose would smell just as good even if it had a different name (``A rose by any other name would smell as sweet'') \\ A Case Study in Paraphrase Targeting Writing Styles}
%\title{“Be super careful on March 15” (“Beware the ides of March”) \\ A Case Study in Paraphrase Targeting Writing Styles}
\title{``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

@@

The same meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.

Paraphrases can differ along many dimensions, including utterance length, diction level, and speech register. 
There is a significant literature in sentence compression aimed at modeling the first of these, length: 
producing meaning-preserving alternations that preserve the meaning of the input string. [citations] 
However, we know of no previous work aimed at modeling meaning-preserving transformations that systematically transform the register or style of an input string. 
Can we learn to reliably map from one form of language to another, transforming formal prose into a more colloquial form, or a casual email into a more formal equivalent?

%Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
%is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines, or allow writers to automatically “upscale” an email before sending it
  \item Enable non-specialists to better understand information in legal or medical documents by translating ``legalese'' or medical jargon into ordinary English.  
  \item Benefit educational applications:
    \begin{enumerate}
    \item Students studying a specific literary style could benefit from access to \emph{modern English} versions of works by authors they are studying.
    \item Automatic register transformations could help students to experiment with writing in the style of the authors they are studying.
    \end{enumerate}
\end{enumerate}

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  In addition we develop several
baseline systems which do not make use of this source of parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or out of
domain parallel monolingual text gathered through Amazon's Mechanical Turk \cite{chen11}.

We evaluate these models both through human judgments and standard evaluation metrics from the machine translation and paraphrase literature.  
However, no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  
We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and 
show that these metrics correlate well with human judgments.

\begin{comment}
Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications.  For example, our systems which generate paraphrases targeting
Shakespearean English could help students to experiment with writing literature in this style.
In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
We therefore present a preliminary investigation into the task of automatically translating Shakespeare's plays into modern English, using our newly developed
automatic evaluation metrics.  By automatically paraphrasing the remaining 20 plays into modern English, 
we believe it should be possible to help make these plays more accessible to students of Shakespeare.
\end{comment}

\section{Shakespearean Paraphrasing}
We use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of 
the most highly-regarded examples of English literature and 
are written in a style that is now 400 years out of date, many linguistic resources are available to help modern readers pick their way through 
these Elizabethan texts. Among these are “translations” of the plays into colloquial English, and dictionaries that provide modern equivalents for specific words and phrases.

We compare 3 different stylistic paraphrase systems targeting Shakespearean English which rely on different types of linguistic resources. 
One leverages parallel “translations”, another exploits dictionary resources, and a third relies on modern, out-of-domain monolingual parallel data and an in-domain corpus.

@@

To generate paraphrases, we apply a typical phrase-based statistical machine translation pipeline, performing
word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.

@@

\subsubsection{Dictionary Based Paraphrase}
\label{dictionary_baseline}
Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based machine
translation.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakespearean paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
  \label{bleupinc}
\end{figure}

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & He killed your relative, brave Mercutio, and then young Romeo killed him. & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & I can read my own fortune in my misery. & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
      %Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
      %\hline
      %Terminator 2 & Terminator & Negative. The T-1000's highest probability for success now would be to copy Sarah Connor and to wait for you to make contact with her. & negative. the t-1000 's most exalted probability for success now would be to have sarah connor and to stay for you to make contact with her . \\
      %\hline
      %Terminator 2 & Terminator & Skynet begins to learn at a geometric rate. ... In a panic, they try to pull the plug. & skynet begins to learn at a geometric rate. ... in a fearful sails , they would pluck the stop . \\
      %\hline
    \end{tabular}
  \end{center}
  \caption{Example Shakespearean paraphrases generated by the best overall system.}
  \label{examples}
\end{table}

@@

These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
trends which are not apparent from the automatic evaluation.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\subsection{Evaluation}
We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments described in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Logistic regression & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics}
  \label{correlation}
\end{table}

@@

Both the cosine and logistic regression style metrics achieve the highest overall correlation with human writing style judgments, with the logistic regression style score performing best.

We note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
  Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
  style scores in the automatic and human evaluations.
}

@@

\section{Translating Shakespeare's Plays to Modern English}
Finally we preform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
benefits to students, as well as translators of Shakespeare's plays into modern English.

@@

These results suggest that in comparison to the dictionary and video corpus baselines, 
our system trained on modern translations generates a large number of paraphrases which match the target style.
Note that the paraphrase system 
based on the out-of-domain video corpus makes very few changes to the input, and thus achieves a very low PINC score.  This is due to the many out of
vocabulary words in Shakespeare's plays which result in very few matching source phrases in the video baseline's phrase table.

@@

\section{Related Work}
Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
In addition several authors have previously proposed 
automatic metrics specifically for evaluating paraphrases \cite{chen11,Callison-Burch08b,liu10}.
We are not aware, however, of any work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however does not investigate the task of paraphrase.  Their generation system
is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
While our work does not address the issue of meter, it should be possible to combine our translation
models with their weighted finite state transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.

@@

\section{Conclusions}
We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespeare's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
perform better according to each criteria.

To address this problem, we have introduced two new metrics for evaluating writing style.
We measured correlation between automatic metrics and human judgments, and showed
that our new metrics have better correlation with human judgments than existing metrics in the context of our task.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating paraphrase systems targeting other writing styles.

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
of Shakespeare and also to human translators.

>>>>

%% Example of a LaTeX source file for a COLING-2012 submission
%% last updated: July 10, 2012
%% Optional instructions for authors within the tex file are provided as comments and start with 'for authors:...'
\documentclass[10pt,a5paper,twoside]{article}
\usepackage{coling2012}
\usepackage{comment}
\usepackage{amsmath}
%\title{Translating to Shakespeare: A Case Study in Paraphrasing Writing Styles}
\title{You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles}
%for authors: in case of more than four author names ref. to commented line below 
%\author{$Annie~SMITH^{1, 2}~~~LI~Xiao Dong^{1, 3}$\\$~~~Third~Author^{1, 2}~~~Fourth~Author^{1, 3}~~~ Fifth~Author^{2, 3}$\\
\author{$Author1^{1, 2}~~~Author2^{1, 3}$\\
{\small  	(1) INSTITUTE\_1, address 1\\ 
 		(2) INSTITUTE\_2, address 2\\
		(3) INSTITUTE\_3, address 3\\
  \texttt{author1@institute1, author@institute2} \\ 
}}

@@

Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.

Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable average people to better consume information by translating legalese or medical jargon into nontechnical English.  
  \item Benefit educational applications, allowing students to:
    \begin{enumerate}
    \item Access \emph{modern English} versions of works by authors they are studying.
    \item Experiment with writing in the style of an author they are studying.
    \end{enumerate}
\end{enumerate}

In this paper, we investigate the task of automatic paraphrasing techniques that target a particular writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We explored several different methods, all of which rely on techniques from phrase-based MT, but which were trained on different types of parallel monolingual data.  The first engine was trained on the text of Shakespeare’s plays, along with parallel modern English “translations” that were written to help students better understand Shakespeare's work.  
%A parallel corpus is extracted from these modern translations,
%which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakespearean English.  
We also developed several
baseline systems which do not make use of this parallel text and instead rely on manually compiled dictionaries of expressions commonly found in Shakespearean English, or existing
corpora of out-of-domain parallel monolingual text.

We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation (MT) and Paraphrase literature, however no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  
We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
preliminary results.

Systems which are capable of automatically paraphrasing literary writing styles could be directly beneficial for educational applications.  For example, our systems which generate paraphrases targeting
Shakespearean English could help students to experiment with writing literature in this style.
In addition, out of the 37 surviving plays written by William Shakespeare, modern translations are currently only available for 17.  
We therefore present a preliminary investigation into the task of automatically translating Shakespeare's plays into modern English, using our newly developed
automatic evaluation metrics.  By automatically paraphrasing the remaining 20 plays into modern English, 
we believe it should be possible to help make these plays more accessible to students of Shakespeare.

\section{Shakespearean Paraphrasing}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivalents.

We compare 3 different stylistic paraphrase systems targeting Shakespearean English which vary in the resources they assume access to.
One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.

@@

To generate paraphrases, we apply a typical phrase-based Statistical Machine Translation pipeline, performing
word alignment on the data described in table \ref{corpus_stats} using GIZA++ \cite{Och03}, then extracting phrase pairs and performing decoding using Moses \cite{Koehn07}.

@@

\subsubsection{Dictionary Based Paraphrase}
\label{dictionary_baseline}
Several dictionaries of stylistically representative words of Shakespearean English and their modern equivalents are available on the web.  
These dictionaries can be used to define a translation model which can be used in combination with a language model as in standard phrase-based Machine
Translation.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.4in]{figures/bleupinc1.pdf} & \includegraphics[width=2.4in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakespearean Paraphrase systems compared using BLEU and PINC.  A brief description of each system is presented in table \ref{systems}.}
  \label{bleupinc}
\end{figure}

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|l|p{1.4in}|p{1.4in}|}
      \hline
      Source & Speaker & Input & Output \\
      \hline
      \hline
      Romeo \& Juliet & Benvolio & He killed your relative, brave Mercutio, and then young Romeo killed him. & he slew thy kinsman , brave mercutio , and then young romeo kill him . \\
      \hline
      Romeo \& Juliet & Romeo & I can read my own fortune in my misery. & i can read mine own fortune in my woes . \\
      \hline
      Star Wars & Palpatine & If you will not be turned, you will be destroyed! & if you will not be turn 'd , you will be undone ! \\
      \hline
      Star Wars & Luke & Father, please! Help me! & father , i pray you , help me ! \\    
      \hline
      The Matrix & Agent Smith & Good bye, Mr. Anderson. & fare you well , good master anderson . \\
      \hline
      The Matrix & Morpheus & I'm trying to free your mind, Neo. But I can only show you the door. You're the one that has to walk through it. & i 'll to free your mind , neo. but i can but show you the door. you 're the one that hath to tread it . \\
      \hline
      Raiders of the Lost Ark & Belloq & Good afternoon, Dr. Jones. & well met , dr. jones . \\
      \hline
      Raiders of the Lost Ark & Jones & I ought to kill you right now. & i should kill thee straight . \\
      \hline
      Terminator 2 & Terminator & My mission is to protect you. & my affair is to keep you . \\
      %\hline
      %Terminator 2 & Terminator & Negative. The T-1000's highest probability for success now would be to copy Sarah Connor and to wait for you to make contact with her. & negative. the t-1000 's most exalted probability for success now would be to have sarah connor and to stay for you to make contact with her . \\
      \hline
      Terminator 2 & Terminator & Skynet begins to learn at a geometric rate. ... In a panic, they try to pull the plug. & skynet begins to learn at a geometric rate. ... in a fearful sails , they would pluck the stop . \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Example Shakespearean paraphrases generated by the best overall system.}
  \label{examples}
\end{table}

@@

These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
trends which are not apparent from the automatic metrics.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\subsection{Evaluation}
We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out Romeo and Juliet), then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments reported in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Maximum Entropy & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics}
  \label{correlation}
\end{table}

@@

Both the Cosine and Maximum Entropy style metrics achieve the highest overall correlation with human writing style judgments, with the Maximum Entropy style score performing significantly better.

Finally we note that overall the automatic metrics tend to agree with agree with human judgments as displayed in figure \ref{style_metrics}.\footnote{
  Although the automatic style metrics rate the dictionary system higher than the video corpus baseline, both systems have very comparable
  style scores in the automatic and human evaluations.
}

@@

\section{Translating Shakespeare's Plays to Modern English}
Finally we preform a preliminary evaluation of the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
benefits to students, as well as translators of Shakespeare's plays into modern English.

@@

The results suggest that in comparison to the dictionary and video corpus baselines, 
our system trained on modern translations generates diverse paraphrases which match the target style.
Note that the paraphrase system 
based on the out-of-domain video corpus makes very few changes to the input, and thus achieves a very low PINC score.  This is due to the many out of
vocabulary words in Shakespeare's plays which result in very few matching source phrases in the video baseline's phrase table.

@@

\section{Related Work}
Although no previous work has investigated paraphrasing modern text into Shakespearean English, or the more general task of paraphrasing while targeting a specific writing
style, we highlight several strands of related work.

Much previous work has addressed the task of automatically generating paraphrases \cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05,Callison-Burch08,Kok10}.  
In addition several authors have previously proposed 
automatic metrics specifically for evaluating paraphrases \cite{chen11,Callison-Burch08b,liu10}.
We are not aware, however, of any previous work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however doesn't address the issue of paraphrase.  Their generation system
is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
While our work does not address the issue of meter, it should be possible to combine our translation
models with their weighted finite state transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.

@@

\section{Conclusions}
We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespeare's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
perform better according to each of these criteria.

To address this problem, we have introduced two new metrics for evaluating writing style.
We measured correlation between automatic metrics and human judgments in the context of paraphrasing writing style, and showed
that our new metrics have better correlation with human judgments than existing metrics in the context of our data.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating paraphrase systems targeting other writing styles.

Finally, we applied these automatic evaluation metrics to an initial investigation into the task of translating Shakespeare's plays into modern English.
We plan to translate the remaining 20 of Shakespeare's plays into modern English, which could be beneficial to students
of Shakespeare's plays and also to human translators.
